\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-08-11 popl-2019-journal-v/paper.tex
Do a pass over discussion of robust hyperproperty preservation paper.

There are other notion of secure compilation than full-abstraction~\citep{abadi_protection_1998}.
\citet{abate_2019} presents an overview of trace-based secure compilation properties.
They show that full-abstraction is a weak notion of secure compilation relatively to other notions, e.g., Robust Relational Hyperproperty Preservation (RrHP) their strongest notion of secure compilation.
However, other notions of secure compilation that promise WBCF and LSE must also enforce it somehow.
\stktokens{} is an enforcement scheme that likely would work for stronger notions of secure compilation.
In fact, we believe that our result could be lifted from full-abstraction to RrHP reusing the back-translation from the full-abstraction proof.

>>>>

There are other notions of secure compilation than full-abstraction~\citep{abadi_protection_1998}.
\citet{abate_2019} present an overview of trace-based secure compilation properties.
Full abstraction is only one, relatively weak, property in their hierarchy.
It would be interesting to investigate if our compiler, i.e.\ the embedding function from \srccm{} into \trgcm{}, also satisfies some of their other properties.
While our current result implies that we can prove contextual equivalences in \trgcm{} components using \stktokens{}, by proving them instead in the more well-behaved \srccm{} semantics, such stronger properties would imply that we can also prove robust preservation of other (hyper-)properties in a similar manner.
We expect that, in addition to full abstraction, our embedding also satisfies Robust Relational Hyperproperty Preservation (RrHP, the strongest property in the hierarchy of \citeauthor{abate_2019}) and that a large part of our current proof (the back-translation and the logical relation) could be reused to establish this.
However, to do this, we would first need to extend our semantics with some form of traces and we have not investigated how best to do this.
